Data analysis to support temporary cycleways

### 2020-04-30 README.Rmd
Add table of contents

---
output: github_document
# uncomment the next line if no phantomjs
# always_allow_html: no
---

@@

# Data analysis to support temporary cycleways

>>>>

---
title: Data analysis to support temporary cycleways
output:
  github_document:
    toc: true
    toc_depth: 2
# uncomment the next line if no phantomjs
# always_allow_html: no
---

@@

# Introduction
